{{< var titll >}}

### 2024-07-08 presentation.qmd
befrev

```{r, echo=F, message=F, warning=F, results='hide'}
library(huxtable)
library(kableExtra)
#Sys.info()[['sysname']]=="Emscripten"
#ManifoldDestiny::wasmconload()
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/20laws40isos.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
modlat <- eqpar$meql
```

>>>>

```{r, echo=F, message=F, warning=F, results='hide'}
library(huxtable)
library(kableExtra)
#Sys.info()[['sysname']]=="Emscripten"
#ManifoldDestiny::wasmconload()
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/20laws40isos.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
modlat <- eqpar$meql
```
